The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex

Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects [\textblue{cite github page}]. These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}). An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset. A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction. The benefits of doing this vary. If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price. If these execute ahead of the market order, the front-runner profits by scalping the price of the shares. If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price. A simpler attack would be to gauge the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information. Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them. Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.

>>>>

Designing truly decentralized exchanges, where the order book is implemented directly on a public blockchain, is being pursued by a number of projects~\cite{inDEXgithub}. These designs generally face the following attack (illustrated in Figure~\ref{fig:RegularFrontrunning}). An adversary can monitor the network with a full node for pending \textit{buy} (or \textit{sell}) transactions which could increase (or \textit{decrease}) the future price of the asset. A front-runner can send a competing orders with a higher gas price, and hope to have her transactions mined ahead of the original pending transaction. The benefits of doing this vary. If the original bid is a large market order (\ie it will execute at any price), the adversary can front-run a pair of limit orders that will bid near the best offer price and offer at a higher price. If these execute ahead of the market order, the front-runner profits by scalping the price of the shares. If the adversary has pre-existing offers likely to be reached by the market order, she could front-run a cancelation and a new offer at a higher price. A simpler attack would be to guage the demand for trades at a given price by the number of pending orders, and to front-run at the same price in hopes that the market demand is the result of accurate new market information. Miners are in the best position to conduct these attacks as they hold fine-grained control over the exact set of transactions that will execute and in what order and can mix in their own (late) transactions without broadcasting them. Miners do however have to commit to what their own transactions will be before beginning the proof of work required to solve a block.
